Calculating Entropies With Nested Sampling

### 2017-02-11 paper/ms.tex
Added check result
More numbers

Letting $\tau = \log_{10} T$, and treating
$A$ and $\phi$ are nuisance parameters, I calculated the entropies
of $\tau$, $\d$, and $(\tau, \d)$.
These results were computed using a tolerance of 0.001 for every quantity.
The results were
\begin{align}
H_{\tau}    &= 7.337 \pm 0.028 \\
H_{\d}      &= 905.9 \pm 1.9   \\ % Interim result only
H_{\tau,\d} &= 902.2 \pm 1.7      % Interim result only
\end{align}

@@

To convert these to differential entropies, we need to add the appropriate
log-volume to each. These are $-6.215$, $-790.32$, and
$-796.53$ respectively, so the differential entropies are:
\begin{align}
H'_{\tau}     &= 1.122 \pm 0.028 % \\
H'_{\d}       &= 115.5 \pm 1.9   \\
H'_{\tau, \d} &= 105.7 \pm 1.7
\end{align}
The mutual information is equal to $H_{\tau} + H_{\d} - H_{\tau, \d}$. The
uncertainties in each of these three quantities is quite large, and would lead
to a large uncertainty on $I_{\tau, \d}$ if computed naively. To reduce this
uncertainty, we computed the three entropies using a common random number
generator for the reference pairs. This is an example of the
{\em common random numbers} technique of variance reduction.
The resulting mutual information is
$I_{\tau, \d} = 11.1 \pm 1.1$ nats {\todo (interim result only)}.

@@

>>>>

Letting $\tau = \log_{10} T$, and treating
$A$ and $\phi$ are nuisance parameters, I calculated the entropies
of $\tau$, $\d$, and $(\tau, \d)$.
These results were computed using a tolerance of 0.001 for every quantity.
The results were
\begin{align}
H_{\tau}    &= 7.337 \pm 0.028 \\
H_{\d}      &= 905.9 \pm 1.9   \\ % Interim result. Check gave 903.3 +- 10.9
H_{\tau,\d} &= 902.2 \pm 1.7      % Interim result only
\end{align}

@@

To convert these to differential entropies, we need to add the appropriate
log-volume to each. These are $-6.215$, $-790.32$, and
$-796.53$ respectively, so the differential entropies are:
\begin{align}
H'_{\tau}     &= 1.122 \pm 0.028 \\
H'_{\d}       &= 115.5 \pm 1.9   \\
H'_{\tau, \d} &= 105.7 \pm 1.7
\end{align}
The mutual information is equal to $H_{\tau} + H_{\d} - H_{\tau, \d}$. The
uncertainties in each of these three quantities is quite large, and would lead
to a large uncertainty on $I_{\tau, \d}$ if computed naively. To reduce this
uncertainty, we computed the three entropies using a common random number
generator for the reference pairs. This is an example of the
{\em common random numbers} technique of variance reduction.
The resulting mutual information is
$I_{\tau, \d} = 11.1 \pm 1.1$ nats {\todo (interim result only)}.

@@

\subsection{Uneven observations}
The results for the uneven observing schedule are
\begin{align}
I_{\x, \d} &= 12.09 \pm 0.82
\end{align}
which appears to be higher than under the even observing schedule,
though the uncertainties
are not small enough to be certain of this.
